Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-11 paper/sec-analysis.tex
added table

Finally, can perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
     Also in this
     case the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

>>>>

We can also perform a similar comparison for
the resolved category.
%
In Fig.~\ref{fig:signal-vs-back-resolved} we compare
the kinematic distributions for signal and background events,
     with and without PU, for the invariant mass and the $p_T$ of the leading
     Higgs candidate.
     %
     Also in this
     case the PU-subtracted background distributions appear reasonably close
     to their no PU counterparts.

@@

To complete this discussion, it is illustrative to determine
which is the mass resolution obtained for the
reconstructed Higgs candidates in various cases.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the invariant mass peak as compared
to the nominal Higgs mass, $\delta m_h$, as well as the
corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of both the leading and subleading Higgs candidates in
the resolved category.
        %
        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction, and the same with SK subtraction.
%
        We find a mass resolution of around 9 GeV in the case
        without PU, which is only slightly degraded
        to around 11 GeV in the case of $\la n_{\rm PU}\ra=80$ PU
        with SK subtraction.
        %
        We also note that, after subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV.

    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{table}[h]
      \centering
      \begin{tabular}{|c|c|c|c|}
        \hline
        &   &   $\delta m_h$  &  $\sigma_{m_h}$  \\
        \hline
        \hline
        \multirow{2}{*}{no PU}  & leading Higgs  &  -3.8 GeV   & 8 GeV   \\
          & subleading Higgs   & -5.8 GeV  &  9 GeV \\
        \hline
          \multirow{2}{*}{$\la n_{\rm PU}\ra=80$}  & leading Higgs  &  +33 GeV   & 9 GeV   \\
          & subleading Higgs   & +31 GeV  &  12 GeV \\
          \hline
            \multirow{2}{*}{$\la n_{\rm PU}\ra=80$+SK}  & leading Higgs  &  +3.9 GeV   & 11 GeV   \\
          & subleading Higgs   & +2.1 GeV  &  11 GeV \\
        \hline
        \end{tabular}
      \caption{\label{tab:massresolution}
        Resolution of the invariant mass distribution of
        reconstructed Higgs candidates in the resolved
        category.
        %
        We show three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction, and the same with SK subtraction.
        %
        We indicate the shift of the invariant mass peak as compared
        to the nominal Higgs mass, $\delta m_h$, as well as the width
        of a Gaussian fitted to the mass distribution, $\sigma_{m_h}$,
        for both the leading and subleading Higgs candidates.
      }
      \end{table}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2015-12-11 paper/sec-mcsamples.tex
added table

Our modelling of detector simulation has been tuned
to lead to a mass resolution of
the reconstructed Higgs candidates of around 10 GeV, consistent
with the hadronic mass resolutions of the
ATLAS and CMS detectors~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb}.
%
By fitting a Gaussian to the 
invariant Higgs mass distributions of 
in signal events, we can 
determine the effective mass resolution
in the present analysis.
%
We find a resolution of about 8\% in the resolved
category, corresponding to a window
of around 10 GeV for $m_h=125$ GeV.
%
Fitting the Higgs    mass distributions 
in the case of $\la n_{\rm PU}\ra=80$ PU events
with subtraction
(see Sect.~\ref{sec:pileup}),
the mass resolution is degraded down to
    around 11\%, corresponding to a windown of
    14 GeV around the Higgs mass.
    %

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Our modelling of detector simulation has been tuned
to lead to a mass resolution of
the reconstructed Higgs candidates consistent
with the hadronic mass resolutions of the
ATLAS and CMS detectors~\cite{Aad:2012gxa,Chatrchyan:2013zna,Aad:2014xzb},
as discussed in Sect.~\ref{sec:pileup}.

%
